A systematic search for transiting planets using \KT

### 2015-02-08 ms.tex
notes for the discussion section

\paragraph{Maybe this goes in results}

@@

To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties.

>>>>

\paragraph{Maybe this goes in results} (Hogg say yes!)

@@

The goal of this \paper\ was to get exoplanet candidates out of the \KT\ pixel-level data,
it was not to generate light curves...
the project does not really produce corrected light curves at all; why not?

This is not the last time the \KT\ data will be searched...
list some deficiencies of this search method
(these might include approximations in the PHIC,
the fact that it deals well with spacecraft systematics but not stellar variability,
and that it isn't sensitive to single transits (which must be common)).

The machine and hand vetting leave much to be desired...
list some deficiencies of the vetting.

Characterization of these candidates can be much improved...
list the things we could know if we had follow-up observations of the stars.

To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties...
Perhaps give a specific example here with some detailed discussion or math.

The completeness and false-positive assessment could be vastly improved...
completeness estimates are not as extensive as desired;
there is essentially no estimate of the non-astrophysical false positive rate.

We have not attempted to do any kind of populations analysis...
but presumably \KT\ data will rock this.  In what ways?
